Description of radiative transfer submodels

### 2019-09-17 analysis/paper/submodel-rtm.Rmd
Add crown area index comparison plots (draft)

plot(ms_out$light_level, type = "l")
lines(ts_out$light_level, col = 2)

plot(ms_out$light_diff_level, type = "l")
lines(ts_out$light_diff_level, col = 2)
```

>>>>

plot(ms_out$light_level, type = "l", lty = "dashed",
     xlab = "Cohort", ylab = "Total light level")
lines(ts_out$light_level, lty = "solid")
legend("topleft", c("2S", "MS"), lty = c("solid", "dashed"))

plot(ms_out$light_diff_level, type = "l", lty = "dashed",
     xlab = "Cohort", ylab = "Diffuse light level")
lines(ts_out$light_diff_level, lty = "solid")
legend("topleft", c("2S", "MS"), lty = c("solid", "dashed"))
```

Run both models under different crown area indices.

ncoh <- 3
ipft <- rep(1, ncoh)
lai <- rep(0.5, ncoh)
cai <- c(0.1, 0.25, 0.5, 1)
colors <- c("red1", "red2", "red3", "black")
ms1 <- lapply(cai, function(.x) multi_scatter(
  ipft, lai, lr[1], lt[1], orient[1], C = .x,
  theta, S0_beam, S0_diff, alb_ground
))
ts1 <- lapply(cai, function(.x) two_stream(
  ipft, lai, lr[1], lt[1], orient[1], cai = .x,
  theta, S0_beam, S0_diff, alb_ground
))
## par(mfrow = c(ncoh, 1))
## for (i in rev(seq_len(ncoh))) {
##   ms1_ll <- vapply(ms1, function(x) x[["light_level"]][i], numeric(1))
##   ts1_ll <- vapply(ts1, function(x) x[["light_level"]][i], numeric(1))
##   matplot(cai, cbind(ts1_ll, ms1_ll), type = "l", col = "black",
##           ylim = c(0.2, 1))
##   legend("topright", c("2S", "MS"), lty = 1:2)
## }

v <- "light_diff_level"
par(mfrow = c(length(cai), 1))
for (i in seq_along(cai)) {
  ms1_ll <- ms1[[i]][[v]]
  ts1_ll <- ts1[[i]][[v]]
  matplot(cbind(ts1_ll, ms1_ll), type = "l", col = "black",
          xlab = "Cohort", ylab = "Total light level",
          ylim = c(0, 0.4), main = paste("CAI = ", cai[i]))
  legend("bottomright", c("2S", "MS"), lty = 1:2)
}
